---
title: "Economically Efficient and Environmentally Sustainable Irrigation Potentials in 2010"
author: "Felicitas Beier"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r Setup, include=FALSE}
# R markdown set-up
knitr::opts_chunk$set(echo = TRUE)

# mr universe functions
library(madrat)
library(magclass)
library(mrwater)
library(mrcommons)

# raster functions 
library(raster)
library(sp)

# terra functions
library(terra)
library(sf) 

# plot functions
library(ggplot2)

# tables for latex
library(xtable)

```

```{r Settings0, include=FALSE}
version  <- "mrwaterFullOutputs"
year     <- "y2010"
scenario <- "ssp2"

# Path
filepath       <- paste0(getwd(), "/inputdata/")
inputdatapath  <- paste0(getwd(), "/inputdata/", version, "/")
outputdatapath <- paste0(getwd(), "/outputs/")

```

## Current Irrigation

```{r ReadinCurrent, include = FALSE, echo = FALSE}
# Current cropland and currently irrigated areas according to LUH
LUHarea      <- setYears(dimSums(read.magpie(paste0(inputdatapath, "cropareaLUH", ".mz")), dim = "MAG"), year)
LUHirrigated <- collapseNames(LUHarea[, , "irrigated"])
LUHtotal     <- dimSums(LUHarea, dim = 3)

# Current irrigated area with EFR=on and off
irrigAreaCurrent <- collapseNames(read.magpie(paste0(inputdatapath, "irrigAreaCurrent.mz"))[,,scenario][,,"irrigatable"][,,"single"])

# water committed to current agricultural use (in mio. m^3) 
watComAg     <- dimSums(read.magpie(paste0(inputdatapath, "watComAg", ".mz")), dim = "crop")
# committed agricultural withdrawal and consumption (in mio. km^3)
watComAgWW   <- collapseNames(watComAg[,,"withdrawal"]) / 1000 
watComAgWC   <- collapseNames(watComAg[,,"consumption"]) / 1000

# Committed agricultural fulfilled uses (in mio. km^3)
comAgWW      <- collapseNames(read.magpie(paste0(inputdatapath, "comAguses.mz"))[,,scenario][,,"currHuman_ww"]) / 1000
comAgWC      <- collapseNames(read.magpie(paste0(inputdatapath, "comAguses.mz"))[,,scenario][,,"currHuman_wc"]) / 1000
comAgWCoff   <- collapseNames(comAgWC[,,"off"])
comAgWCon    <- collapseNames(comAgWC[,,"on"])

# Non-agricultural uses (in mio. km^3)
watNonAgWW   <- collapseNames(read.magpie(paste0(inputdatapath, "nonAguses.mz"))[,,scenario][,,"currHuman_ww"]) / 1000
watNonAgWC   <- collapseNames(read.magpie(paste0(inputdatapath, "nonAguses.mz"))[,,scenario][,,"currHuman_wc"]) / 1000
```

```{r ReportCurrentArea, include=TRUE, echo=FALSE}
writeLines(paste0("Globally, an area of ", round(dimSums(LUHirrigated, dim = 1)), " Mha is reported to be irrigated according to LUH. \nOf these irrigated areas, ", round(dimSums(irrigAreaCurrent[,,"off"], dim = 1)), " Mha could be fulfilled \ngiven the local water availability in this study. \nIF EFR were to be maintained, it would be ", round(dimSums(irrigAreaCurrent[,,"on"], dim = 1)), " Mha.")) 
```

```{r ReportCurrentVolume, include=TRUE, echo=FALSE}
writeLines(paste0("Globally, a consumptive water volume of ", round(dimSums(watComAgWC, dim = 1)), " km3/yr is required to irrigate \nthe given cropmix (FAO country-level production pattern of 2010) on currently irrigated areas to its full potential. \nOf these irrigation water requirements, ", round(dimSums(comAgWCoff, dim = 1)), " km3/yr could be fulfilled \ngiven the local water availability in this study. \nThis volume would be reduced to ", round(dimSums(comAgWCon, dim = 1)), " km3/yr if the EFR were to be maintained."))
```

To calculate total (un)sustainable water uses in order to compare the value with the planetary boundary, 
the following non-agricultural uses have to be added to the Irrigation Potentials, respectively:

```{r NonAgUses, include=TRUE, echo=FALSE}
print(paste0("Global non-ag. consumption (unsustainable): ", round(dimSums(watNonAgWC[,,"off"], dim = 1)), " km^3/yr"))
print(paste0("Global non-ag. consumption (sustainable): ", round(dimSums(watNonAgWC[,,"on"], dim = 1)), " km^3/yr"))
```


## Aggregated Economic Irrigation Potentials

For the correct interpretation of the marginal return to irrigation,
the committed agricultural uses river routing iteration must be switched off.
Otherwise, these areas are pre-reserved and their reported willingness-to-pay 
for irrigation would not represent the true value of irrigation
in these locations. 

The following section uses the results of a run with deactivated committed
agricultural uses for the creation of country results (tables for the 
supplementary material) and the country- and basin-level IAD curves. 

```{r SCENARIOdata, include=FALSE, echo=FALSE}
# Current irrigated area (ACTUAL)
IrrigAreaEconACTSUS    <- read.magpie(paste0(inputdatapath, "IrrigAreaEconACTSUS", ".mz"))
IrrigAreaEconACTUNSUS  <- read.magpie(paste0(inputdatapath, "IrrigAreaEconACTUNSUS", ".mz"))

wat_ag_wcEconACTSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconACTSUS", ".mz"))
wat_ag_wcEconACTUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconACTUNSUS", ".mz"))

wat_ag_wwEconACTSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconACTSUS", ".mz"))
wat_ag_wwEconACTUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconACTUNSUS", ".mz"))

yieldgainareaACTunsus  <- read.magpie(paste0(inputdatapath, "yieldgainarea_actUNSUS.mz"))
yieldgainareaACTsus    <- read.magpie(paste0(inputdatapath, "yieldgainarea_actSUS.mz"))

yieldgainwaterACTunsus <- read.magpie(paste0(inputdatapath, "yieldgainwater_actUNSUS.mz")) / 1000
yieldgainwaterACTsus   <- read.magpie(paste0(inputdatapath, "yieldgainwater_actSUS.mz")) / 1000

# Current cropland area (CUR)
IrrigAreaEconCURSUS    <- read.magpie(paste0(inputdatapath, "IrrigAreaEconCURSUS", ".mz"))
IrrigAreaEconCURUNSUS  <- read.magpie(paste0(inputdatapath, "IrrigAreaEconCURUNSUS", ".mz"))

wat_ag_wcEconCURSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconCURSUS", ".mz"))
wat_ag_wcEconCURUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconCURUNSUS", ".mz"))

wat_ag_wwEconCURSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconCURSUS", ".mz"))
wat_ag_wwEconCURUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconCURUNSUS", ".mz"))

yieldgainareaCURunsus  <- read.magpie(paste0(inputdatapath, "yieldgainarea_curUNSUS.mz"))
yieldgainareaCURsus    <- read.magpie(paste0(inputdatapath, "yieldgainarea_curSUS.mz"))

yieldgainwaterCURunsus <- read.magpie(paste0(inputdatapath, "yieldgainwater_curUNSUS.mz")) / 1000
yieldgainwaterCURsus   <- read.magpie(paste0(inputdatapath, "yieldgainwater_curSUS.mz")) / 1000

# Potential cropland area (POT)
IrrigAreaEconPOTSUS    <- read.magpie(paste0(inputdatapath, "IrrigAreaEconPOTSUS", ".mz"))
IrrigAreaEconPOTUNSUS  <- read.magpie(paste0(inputdatapath, "IrrigAreaEconPOTUNSUS", ".mz"))

wat_ag_wcEconPOTSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconPOTSUS", ".mz"))
wat_ag_wcEconPOTUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconPOTUNSUS", ".mz"))

wat_ag_wwEconPOTSUS    <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconPOTSUS", ".mz"))
wat_ag_wwEconPOTUNSUS  <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconPOTUNSUS", ".mz"))

yieldgainareaPOTunsus  <- read.magpie(paste0(inputdatapath, "yieldgainarea_potUNSUS.mz"))
yieldgainareaPOTsus    <- read.magpie(paste0(inputdatapath, "yieldgainarea_potSUS.mz"))

yieldgainwaterPOTunsus <- read.magpie(paste0(inputdatapath, "yieldgainwater_potUNSUS.mz")) / 1000
yieldgainwaterPOTsus   <- read.magpie(paste0(inputdatapath, "yieldgainwater_potSUS.mz")) / 1000

```

```{r OverviewTables, include=FALSE, echo=FALSE}
# Extract reported yield value gain thresholds
gt <- getNames(collapseNames(IrrigAreaEconACTSUS[,,"on"]))

## Irrigated Area (PIA = Potentially Irrigated Areas) [mio. ha]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainareaACTunsus[,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainareaCURunsus[,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainareaPOTunsus[,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIA <- data
  } else {
    PIA <- rbind(PIA, data)
  }
  i <- i + 1
}

## Irrigated Water Consumption (PIWC = Potential Irrigation Water Consumption) [mio. m^3]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainwaterACTunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterCURunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterPOTunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIWC <- data
  } else {
    PIWC <- rbind(PIWC, data)
  }
  i <- i + 1
}



## Irrigated Water Withdrawals (PIWW = Irrigation Water Withdrawal Potentials) [mio. m^3]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainwaterACTunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTUNSUS[,,"off"][,,"0"], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterCURunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterPOTunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTUNSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTUNSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTSUS[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTSUS[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIWW <- data
  } else {
    PIWW <- rbind(PIWW, data)
  }
  i <- i + 1
}

# Write country results to csv
write.csv(x = PIA, 
          file = paste0(outputdatapath, "PIA_bycountry.csv"), 
          row.names = FALSE)
write.csv(x = PIWW, 
          file = paste0(outputdatapath, "PIWW_bycountry.csv"), 
          row.names = FALSE)
write.csv(x = PIWC, 
          file = paste0(outputdatapath, "PIWC_bycountry.csv"),
          row.names = FALSE)

```

```{r GlobalOverviewTable, include=FALSE, echo=FALSE}

tmp <- NULL
for (g in c(0, 500)) {
  
  global <- data.frame(Scenario = "ACT", 
                       PIA = round(sum(PIA$ACT[PIA$GT==g])), 
                       PIWC = round(sum(PIWC$ACT[PIWC$GT==g])), 
                       PIWW = round(sum(PIWW$ACT[PIWW$GT==g])))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-UNSUS", 
                             PIA = round(sum(PIA$ACT.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-WATSUS", 
                             PIA = round(sum(PIA$ACT.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-LANDSUS", 
                             PIA = round(sum(PIA$ACT.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-SUS", 
                             PIA = round(sum(PIA$ACT.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.SUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR", 
                             PIA = round(sum(PIA$CUR[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-UNSUS", 
                             PIA = round(sum(PIA$CUR.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-WATSUS", 
                             PIA = round(sum(PIA$CUR.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-LANDSUS", 
                             PIA = round(sum(PIA$CUR.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-SUS", 
                             PIA = round(sum(PIA$CUR.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.SUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT", 
                             PIA = round(sum(PIA$POT[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-UNSUS", 
                             PIA = round(sum(PIA$POT.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-WATSUS", 
                             PIA = round(sum(PIA$POT.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-LANDSUS", 
                             PIA = round(sum(PIA$POT.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-SUS", 
                             PIA = round(sum(PIA$POT.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.SUS[PIWW$GT==g]))))
  
  global$gainthreshold <- g
  
  tmp <- rbind(tmp, global)

}

global <- reshape(tmp, idvar = "Scenario", timevar = "gainthreshold", direction = "wide")

print(xtable(global, type = "latex", file = "table.tex", digits = 0, align = c("l", "|l|", "r", "r", "r|", "r", "r", "r|"), label = "Tabl:IrrigationPotentials", caption = "Potentially irrigated areas (PIA), irrigation water consumption potentials (PIWC) and irrigation water withdrawal potentials (PIWW) for different scenarios. Technical irrigation potential (A) refers to the irrigation potential at a yield value gain threshold of at least 0 USD/ha. Economic irrigation potential (B) refers to the irrigation potential at a yield value gain threshold of at least 500 USD/ha"), include.rownames= FALSE)

write.csv(x = global, 
          file = paste0(outputdatapath, "Global", ".csv"), 
          row.names = FALSE)
```

```{r IADcurveInTextNumbers, include=TRUE, echo=FALSE}

# Available irrigation area on potential cropland
avlArea <- read.magpie(paste0(inputdatapath, "avlIrrigarea_pot.mz"))

### Read in data ###
currCroplandSUS   <- collapseNames(IrrigAreaEconCURSUS[, , "on"])
potCroplandSUS    <- collapseNames(IrrigAreaEconPOTSUS[, , "on"])
currCroplandUNSUS <- collapseNames(IrrigAreaEconCURUNSUS[, , "off"])
potCroplandUNSUS  <- collapseNames(IrrigAreaEconPOTUNSUS[, , "off"])
currYieldgain1    <- read.magpie(paste0(inputdatapath, "yieldgainarea_curUNSUS.mz"))
potYieldgain1     <- read.magpie(paste0(inputdatapath, "yieldgainarea_potUNSUS.mz"))

# In-text numbers
print(paste0("In Mexico, ", round(dimSums(LUHtotal["MEX",,], dim = 1), digits = 1), "of total cropland are available."))
print(paste0(round(dimSums(currYieldgain1["MEX", , "500"], dim = c(1,3)), digits = 1), " would provide a yield value gain greater than 500."))
print(paste0(round(dimSums(currCroplandSUS["MEX", , "500"], dim = c(1,3)), digits = 1), " could be sustainably irrigated."))
print(paste0(round(dimSums(currCroplandUNSUS["MEX", , "500"], dim = c(1,3)), digits = 1), " could be unsustainably irrigated."))
print(paste0("Currently, LUH reports ", round(dimSums(LUHirrigated["MEX",,], dim = 1), digits = 1), " to be irrigated."))
print(paste0("Of non-protected areas in Mexico (", round(dimSums(avlArea["MEX",,], dim = 1), digits = 1), " Mha), "))
print(paste0(round(dimSums(potYieldgain1["MEX",,"500"], dim = c(1,3)), digits = 1), " have a yield gain above 500 USD/ha,"))
print(paste0("but only ", round(dimSums(potCroplandSUS["MEX",,"500"], dim = c(1,3)), digits = 1), " could be sustainably irrigated,"))
print(paste0("and only ", round(dimSums(potCroplandUNSUS["MEX",,"500"], dim = c(1,3)), digits = 1), " could be unsustainably irrigated"))

print(paste0("Globally, ", round(dimSums(LUHtotal, dim = 1), digits = 1), "of total cropland are available."))
print(paste0(round(dimSums(currYieldgain1[, , "500"], dim = c(1,3)), digits = 1), " would provide a yield value gain greater than 500."))
print(paste0(round(dimSums(currCroplandSUS[, , "500"], dim = c(1,3)), digits = 1), " could be sustainably irrigated."))
print(paste0(round(dimSums(currCroplandUNSUS[, , "500"], dim = c(1,3)), digits = 1), " could be unsustainably irrigated."))
print(paste0("Currently, LUH reports ", round(dimSums(LUHirrigated, dim = 1), digits = 1), " to be irrigated globally."))
print(paste0("Of global non-protected areas (", round(dimSums(avlArea, dim = 1), digits = 1), " Mha), "))
print(paste0(round(dimSums(potYieldgain1[,,"500"], dim = c(1,3)), digits = 1), " have a yield gain above 500 USD/ha,"))
print(paste0("but only ", round(dimSums(potCroplandSUS[,,"500"], dim = c(1,3)), digits = 1), " could be sustainably irrigated,"))
print(paste0("and only ", round(dimSums(potCroplandUNSUS[,,"500"], dim = c(1,3)), digits = 1), " could be unsustainably irrigated"))    

```

```{r IADcurveFunctionSUSvUNSUS, include=TRUE, echo=FALSE}
    
plotIADcurve <- function(version     = "HalfEarth",
                         aggregation = "countries") {

  ### Aggregate and rearrange data ###
  if (aggregation == "countries") {

    df   <- as.data.frame(dimSums(currCroplandSUS, dim = c(1.1, 1.2)))
    df$IrrigArea <- "Sustainable \nIrrigation Area Potential \non current cropland \n(CUR-SUS)"

    tmp    <- as.data.frame(dimSums(potCroplandSUS, dim = c(1.1, 1.2)))
    tmp$IrrigArea <- "Sustainable \nIrrigation Area Potential \non potential cropland \n(POT-SUS)"
    df <- rbind(df, tmp)

    tmp    <- as.data.frame(dimSums(currCroplandUNSUS, dim = c(1.1, 1.2)))
    tmp$IrrigArea <- "Unsustainable \nIrrigation Area Potential \non current cropland \n(CUR-UNSUS)"
    df <- rbind(df, tmp)

    tmp    <- as.data.frame(dimSums(potCroplandUNSUS, dim = c(1.1, 1.2)))
    tmp$IrrigArea <- "Unsustainable \nIrrigation Area Potential \non potential cropland \n(POT-UNSUS)"
    df <- rbind(df, tmp)

    df <- data.frame(Region = df$Region,
                     GT = as.numeric(as.character(df$Data1)),
                     Group = df$IrrigArea,
                     IrrigArea = df$Value,
                     stringsAsFactors = FALSE)
    df$LUHIrrigated <- rep(as.array(dimSums(LUHirrigated, dim = c(1.1, 1.2))), length(df$Group) / length(as.array(dimSums(LUHirrigated, dim = c(1.1, 1.2)))))
    df$LUHCropland <- rep(as.array(dimSums(LUHtotal, dim = c(1.1, 1.2))), length(df$Group) / length(as.array(dimSums(LUHtotal, dim = c(1.1, 1.2)))))

    df <- df[df$Region %in% c("CHN", "IND", "AUS", "USA", "MEX", "BRA", "ITA", "TUR", "SDN"), ]
    df$Region <- factor(df$Region, levels = c("CHN", "IND", "AUS", "USA", "MEX", "BRA", "ITA", "TUR", "SDN"))
    
  } else if (aggregation == "basins") {

    selectedBasins <- c("Chang Jiang", "Huang He", "Mekong",
                        "Mississippi", "Colorado", "Murray",
                        "Parana", "Ganges", "Indus")

    framestructure <- as.data.frame(new.magpie(cells_and_regions = selectedBasins,
                                               years = getYears(currCroplandSUS),
                                               names = getNames(currCroplandSUS)))
    df <- framestructure
    for (b in selectedBasins) {
      df$Value[df$Region == b] <- dimSums(currCroplandSUS[toolSelectRiverBasin(basinname = b), , ], dim = 1)
    }
    df$Group <- "Sustainable \nIrrigation Area Potential \non current cropland \n(CUR-SUS)"

    tmp <- framestructure
    for (b in selectedBasins) {
      tmp$Value[tmp$Region == b] <- dimSums(potCroplandSUS[toolSelectRiverBasin(basinname = b), , ], dim = 1)
    }
    tmp$Group <- "Sustainable \nIrrigation Area Potential \non potential cropland \n(POT-SUS)"
    df <- rbind(df, tmp)

    tmp <- framestructure
    for (b in selectedBasins) {
      tmp$Value[tmp$Region == b] <- dimSums(currCroplandUNSUS[toolSelectRiverBasin(basinname = b), , ], dim = 1)
    }
    tmp$Group <- "Unsustainable \nIrrigation Area Potential \non current cropland \n(CUR-UNSUS)"
    df <- rbind(df, tmp)

    tmp <- framestructure
    for (b in selectedBasins) {
      tmp$Value[tmp$Region == b] <- dimSums(potCroplandUNSUS[toolSelectRiverBasin(basinname = b), , ], dim = 1)
    }
    tmp$Group <- "Unsustainable \nIrrigation Area Potential \non potential cropland \n(POT-UNSUS)"
    df <- rbind(df, tmp)
  
    df <- data.frame(Region = df$Region,
                     GT = as.numeric(as.character(df$Data1)),
                     Group = df$Group,
                     IrrigArea = df$Value,
                     stringsAsFactors = FALSE)

    tmp <- framestructure
    for (b in selectedBasins) {
      tmp$Value[tmp$Region == b] <- dimSums(LUHirrigated[toolSelectRiverBasin(basinname = b), , ], dim = 1)
      tmp$Value1[tmp$Region == b] <- dimSums(LUHtotal[toolSelectRiverBasin(basinname = b), , ], dim = 1)
    }
    df$LUHIrrigated <- tmp$Value
    df$LUHCropland  <- tmp$Value1
    df$Region <- factor(df$Region, levels = selectedBasins)

  } else {
    stop("Chosen aggregation is not yet implemented")
  }

  ### Plot ###
  out <- ggplot(df, aes(x = IrrigArea, y = GT, color = Group, group = Group, shape = Group)) +
                geom_line(aes(linetype = Group), size = 1.5) +
                geom_point(size = 3) +
                geom_point(aes(x = LUHIrrigated, y = 0), size = 5, color = "black", shape = 17) +
                facet_wrap(~Region, scales = "free_x") +
                scale_color_manual(values = c("#1b9e77", "#d95f02", "#1b9e77", "#d95f02")) +
                scale_linetype_manual(values = c("solid", "solid", "dashed", "dashed")) +
                scale_shape_manual(values = c(19, 13, 19, 13)) +
                scale_x_continuous(expand = c(0, 0)) +
                scale_y_continuous(expand = c(0, 0)) +
                xlab("Irrigation Area Potential (in Mha)") + ylab("Irrigation yield value gain (in USD/ha)") +
                theme_bw() +
                theme(legend.title         = element_blank(),
                      legend.position      = "bottom",
                      legend.text          = element_text(size = 12),
                      legend.key.width     = unit(2.8, "line"),
                      legend.justification = c(0, 1),
                      legend.margin        = margin(t = 0, r = 0, b = 0, l = -77, unit = "pt"),
                      strip.text           = element_text(size = 18),
                      strip.background     = element_rect(fill = "#f6f6f6"),
                      plot.title           = element_text(size = 18),
                      axis.text.x          = element_text(size = 16),
                      axis.title.x         = element_text(size = 18),
                      axis.text.y          = element_text(size = 16),
                      axis.title.y         = element_text(size = 18),
                      panel.grid.major.x   = element_blank(),
                      panel.grid.minor.x   = element_blank())
  ggsave(paste0(outputdatapath, aggregation, "_Curves.pdf"), plot = out, width = 297, height = 210, units = "mm")
  
  return(out)
}

```

```{r PlotAggregateFull, include=FALSE, echo=FALSE}

plotIADcurve(version = version, aggregation = "countries")

plotIADcurve(version = version, aggregation = "basins")

```



## Global Irrigation Potentials

When analyzing irrigation potentials of current or historic time periods, 
the current agricultural use reservation option should be included
because current human water abstractions for irrigated agriculture divert 
river flows and should be considered in the assessment of cellular discharge.

The following section used a model run where the current agricultural use 
river routing iteration is activated.
It is the basis for the global summary table, the irrigation potential maps and
additional country tables of the Supplementary Material. 


```{r SCENARIOdataCOMAG, include=FALSE, echo=FALSE}
# Current irrigated area (ACTUAL)
IrrigAreaEconACTSUScomAg   <- read.magpie(paste0(inputdatapath, "IrrigAreaEconACTSUScomAg", ".mz"))
IrrigAreaEconACTUNSUScomAg <- read.magpie(paste0(inputdatapath, "IrrigAreaEconACTUNSUScomAg", ".mz"))

wat_ag_wcEconACTSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconACTSUScomAg", ".mz"))
wat_ag_wcEconACTUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconACTUNSUScomAg", ".mz"))

wat_ag_wwEconACTSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconACTSUScomAg", ".mz"))
wat_ag_wwEconACTUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconACTUNSUScomAg", ".mz"))

# Current cropland area (CUR)
IrrigAreaEconCURSUScomAg   <- read.magpie(paste0(inputdatapath, "IrrigAreaEconCURSUScomAg", ".mz"))
IrrigAreaEconCURUNSUScomAg <- read.magpie(paste0(inputdatapath, "IrrigAreaEconCURUNSUScomAg", ".mz"))

wat_ag_wcEconCURSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconCURSUScomAg", ".mz"))
wat_ag_wcEconCURUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconCURUNSUScomAg", ".mz"))

wat_ag_wwEconCURSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconCURSUScomAg", ".mz"))
wat_ag_wwEconCURUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconCURUNSUScomAg", ".mz"))

# Potential cropland area (POT)
IrrigAreaEconPOTSUScomAg   <- read.magpie(paste0(inputdatapath, "IrrigAreaEconPOTSUScomAg", ".mz"))
IrrigAreaEconPOTUNSUScomAg <- read.magpie(paste0(inputdatapath, "IrrigAreaEconPOTUNSUScomAg", ".mz"))

wat_ag_wcEconPOTSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconPOTSUScomAg", ".mz"))
wat_ag_wcEconPOTUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wcEconPOTUNSUScomAg", ".mz"))

wat_ag_wwEconPOTSUScomAg   <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconPOTSUScomAg", ".mz"))
wat_ag_wwEconPOTUNSUScomAg <- read.magpie(paste0(inputdatapath, "wat_ag_wwEconPOTUNSUScomAg", ".mz"))

```

```{r OverviewTablesCOMAG, include=FALSE, echo=FALSE}
# Extract reported yield value gain thresholds
gt <- getNames(collapseNames(IrrigAreaEconACTSUScomAg[,,"on"]))

## Irrigated Area (PIA = Irrigation Area Potential) [mio. ha]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainareaACTunsus[,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTUNSUScomAg[,,"off"][,,"0"], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconACTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainareaCURunsus[,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconCURSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainareaPOTunsus[,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(IrrigAreaEconPOTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIA <- data
  } else {
    PIA <- rbind(PIA, data)
  }
  i <- i + 1
}

## Irrigated Water Consumption (PIWC = Irrigation Water Consumption Potentials) [mio. km^3]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainwaterACTunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTUNSUScomAg[,,"off"][,,"0"], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconACTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterCURunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconCURSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterPOTunsus[,,"consumption"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wcEconPOTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIWC <- data
  } else {
    PIWC <- rbind(PIWC, data)
  }
  i <- i + 1
}



## Irrigated Water Withdrawals (PIWW = Irrigation Water Withdrawal Potentials) [mio. km^3]
i <- 0

for (g in gt) {

  # Actually Irrigated Land
  data <- as.data.frame(dimSums(yieldgainwaterACTunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  data <- data.frame(Country = data$Region, "ACT" = data$Value, GT = g)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTUNSUScomAg[,,"off"][,,"0"], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconACTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "ACT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Current Cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterCURunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconCURSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "CUR-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  # Potential cropland
  tmp  <- as.data.frame(dimSums(yieldgainwaterPOTunsus[,,"withdrawal"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTUNSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-UNSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTUNSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-WATSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTSUScomAg[,,"off"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-LANDSUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  tmp  <- as.data.frame(dimSums(wat_ag_wwEconPOTSUScomAg[,,"on"][,,g], dim = c(1.1, 1.2)))
  tmp  <- data.frame(Country = tmp$Region, "POT-SUS" = tmp$Value, GT = g)
  data <- merge(data, tmp)
  
  if (i == 0) {
    PIWW <- data
  } else {
    PIWW <- rbind(PIWW, data)
  }
  i <- i + 1
}

# Write country results to csv
write.csv(x = PIA, 
          file = paste0(outputdatapath, "PIA_bycountry_comAg.csv"), 
          row.names = FALSE)
write.csv(x = PIWW, 
          file = paste0(outputdatapath, "PIWW_bycountry_comAg.csv"), 
          row.names = FALSE)
write.csv(x = PIWC, 
          file = paste0(outputdatapath, "PIWC_bycountry_comAg.csv"),
          row.names = FALSE)

```

```{r GlobalOverviewTablecomAg, include=FALSE, echo=FALSE}

tmp <- NULL
for (g in c(0, 500)) {
  
  global <- data.frame(Scenario = "ACT", 
                       PIA = round(sum(PIA$ACT[PIA$GT==g])), 
                       PIWC = round(sum(PIWC$ACT[PIWC$GT==g])), 
                       PIWW = round(sum(PIWW$ACT[PIWW$GT==g])))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-UNSUS", 
                             PIA = round(sum(PIA$ACT.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-WATSUS", 
                             PIA = round(sum(PIA$ACT.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-LANDSUS", 
                             PIA = round(sum(PIA$ACT.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "ACT-SUS", 
                             PIA = round(sum(PIA$ACT.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$ACT.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$ACT.SUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR", 
                             PIA = round(sum(PIA$CUR[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-UNSUS", 
                             PIA = round(sum(PIA$CUR.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-WATSUS", 
                             PIA = round(sum(PIA$CUR.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-LANDSUS", 
                             PIA = round(sum(PIA$CUR.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "CUR-SUS", 
                             PIA = round(sum(PIA$CUR.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$CUR.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$CUR.SUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT", 
                             PIA = round(sum(PIA$POT[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-UNSUS", 
                             PIA = round(sum(PIA$POT.UNSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.UNSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.UNSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-WATSUS", 
                             PIA = round(sum(PIA$POT.WATSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.WATSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.WATSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-LANDSUS", 
                             PIA = round(sum(PIA$POT.LANDSUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.LANDSUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.LANDSUS[PIWW$GT==g]))))
  global <- rbind(global, 
                  data.frame(Scenario = "POT-SUS", 
                             PIA = round(sum(PIA$POT.SUS[PIA$GT==g])), 
                             PIWC = round(sum(PIWC$POT.SUS[PIWC$GT==g])), 
                             PIWW = round(sum(PIWW$POT.SUS[PIWW$GT==g]))))
  
  global$gainthreshold <- g
  
  tmp <- rbind(tmp, global)

}

global <- reshape(tmp, idvar = "Scenario", timevar = "gainthreshold", direction = "wide")

write.csv(x = global, 
          file =  paste0(outputdatapath, "Global_comAg", ".csv"), 
          row.names = FALSE)

```


## Maps

The following section creates the maps using the Equal Earth projection
to provide an equal area visualization.  

```{r LandMaskTerra, include=FALSE}
# Standard projection of MAgPIE object
LatLonProj <- "+proj=longlat +datum=WGS84"
# Equal Earth projection
NewProj    <- "+proj=eqearth +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
# Map extent
ylim       <- c(-6500000, 8300000)
xlim       <- c(-12577316, 15581284)

### Handle vector data (country shape file and land mask) with terra package ###
# Country borders from Natural Earth Data (http://www.naturalearthdata.com/downloads/10m-cultural-vectors/). accessed on Dec. 13th 2021
worldCountries <- terra::vect(paste0(filepath, "ne_10m_admin_0_countries.shp"))
worldCountries <- terra::project(worldCountries, NewProj)

# Create land mask for pretty continent borders
landMask       <- terra::as.polygons(ext(worldCountries))
landMask       <- terra::symdif(landMask, worldCountries)

# Note: terra cannot transform raster object to Equal-Earth projection yet
.toolRasterTransform <- function(x) {
  
  x0  <- as.RasterBrick(x)
  out <- raster::projectRaster(x0, crs = crs(NewProj), over = TRUE)

  return(out)
}
```

For visualization purposes, areas with very little cropland area (cropland < 1 percent of cell area) are excluded from maps showing current areas.
For maps showing potential cropland areas, areas with potential irrigation area < 1 percent of the cell area are excluded. 

```{r ExclusionOfSmallAreas, include=FALSE, echo=FALSE}

mapping            <- toolGetMapping("LPJ_CellBelongingsToCountries.csv", type = "cell")
cellarea           <- (111e3 * 0.5) * (111e3 * 0.5) * cos(mapping$lat / 180 * pi) / 10000000000 # square meter -> Mha (1ha = 10000m^2)
cellarea           <- as.magpie(cellarea, spatial = 1)
magclass::getCells(cellarea) <- magclass::getCells(LUHtotal)

# share of cropland of total cell area
croplandcellshare <- LUHtotal / cellarea

# share potentially irrigated of total cell area
irrigcellshare    <- avlArea / cellarea

```

# Current Irrigation

The Fulfilled-Share-Map shows the share of current irrigation water demand under full irrigation requirements (ACTUAL) that can be fulfilled by locally available renewable water resources captured in our data set (ACT-UNSUS). 

```{r ReadInCurrent, include=FALSE, echo=FALSE}
# Input data
input <- "shrCurrIrrigFulfilled"

# Read in data
x <- collapseNames(read.magpie(paste0(inputdatapath, input, ".mz"))[, year, "off.ssp2"])

# Exclude very small cropland areas
x[croplandcellshare < 0.01] <- NA

# Transform to raster for plotting
x1 <- .toolRasterTransform(x)

# Plot settings
legendcolor  <- c("#a50026", "#d73027", "#f46d43", "#fdae61", "#fee090",
                  "#e0f3f8", "#abd9e9", "#74add1", "#4575b4", "#313695") 
colNA        <- "#d9d9d9"
legendlimit  <- c(0, 1)
legendbreaks <- seq(0, 1, 0.1)


# Plot and save
pdf(paste0(outputdatapath, input, ".pdf"), width = 26, height = 15)

  # Main plot
  plot(landMask, col = "white", border = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
  plot(x1, ylim = ylim, xlim = xlim,  asp = NA, axes = FALSE, 
       legend = FALSE,
       col = legendcolor,
       colNA = colNA,
       breaks = legendbreaks,
       add = T)
  plot(landMask, col = "white", border = "white", ylim = ylim, xlim = xlim,  asp = NA, axes = FALSE, add = T)
  plot(worldCountries, ylim = ylim, xlim = xlim,  asp = NA, axes = FALSE, add = T)
  
  # Legend
    plot(x1,
       legend.only   = TRUE,
       horizontal    = TRUE,
       col           = legendcolor,
       breaks        = legendbreaks,
       colNA         = colNA,
       legend.args   = list(text = "Fulfilled Share", side = 3, font = 1, line = 2, cex = 4),
       axis.args     = list(cex.axis = 4, at = legendbreaks, line = 0, tick = FALSE, hadj = 0.5, padj = 0.5),
       smallplot     = c(0.4, 0.75, 0.05, 0.1),
       add = T)


dev.off()

```


# Technical Irrigation Potentials

The Technical Irrigation Potentials map shows the irrigation potential at a yield value gain threshold of 0 on current cropland (b) and potential cropland (c) compared to actually irrigated areas according to LUH (a). 

```{r PlotTechnical, include=FALSE, echo=FALSE}
filename <- "IrrigAreaOverview"

# Area correction (only show areas where there is available irrigation area > 1% of cell size)
irrigcellshare[irrigcellshare < 0.01] <- 0

a <- collapseNames(IrrigAreaEconACTSUScomAg[,,"0.off"])
b <- collapseNames(IrrigAreaEconCURSUScomAg[,,"0.off"])
c <- collapseNames(IrrigAreaEconPOTSUScomAg[,,"0.off"])

a[irrigcellshare == 0] <- NA
b[irrigcellshare == 0] <- NA
c[irrigcellshare == 0] <- NA

# Legend range adjustment (cell share rather than Mha)
a <- a / cellarea
b <- b / cellarea
c <- c / cellarea
legendtitle  <- "Cellshare"
legendbreaks <- seq(0, 1, 0.1)
legendcolor  <- c("#FFFFFF", "#f7fcb9", "#e5f5e0", "#c7e9c0", "#a1d99b", 
                  "#74c476", "#41ab5d", "#238b45", "#006d2c", "#00441b")

# Transform magpie object to raster object
a <- .toolRasterTransform(x = a)
b <- .toolRasterTransform(x = b)
c <- .toolRasterTransform(x = c)

jpeg(paste0(outputdatapath, filename, ".jpeg"), width = 8, height = 13.5, units = "in", res = 400)

par(mar = c(3, 2, 2, 2), 
    mfrow = c(3, 1), 
    bg = "transparent")

### Graph 1: LUH irrigated area (sustainable)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
plot(a, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = legendcolor,
     breaks       = legendbreaks,
     colNA        = colNA,
     add          = T)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
title("(a) Currently irrigated areas", outer = FALSE, cex.main = 2.5, line = 0.5)

### Graph 2: Irrigation Area Potentials (sustainable) on current cropland
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
plot(b, ylim = ylim, xlim = xlim,
     legend       = FALSE,
     col          = legendcolor,
     breaks       = legendbreaks,
     colNA        = "#d9d9d9",
     add          = T)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
title("(b) Irrigation area potential on current cropland", outer = FALSE, cex.main = 2.5, line = 0.5)

### Graph 3: Irrigation Area Potentials (sustainable) on potential cropland
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
plot(c, ylim = ylim, xlim = xlim,
     legend       = FALSE,
     col          = legendcolor,
     breaks       = legendbreaks,
     colNA        = "#d9d9d9",
     add          = T)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
title("(c) Irrigation area potential on potential cropland", outer = FALSE, cex.main = 2.5, line = 0.5)

# Legend
plot(c, bg = "transparent",
     legend.only   = TRUE,
     horizontal    = TRUE,
     col           = legendcolor,
     breaks        = legendbreaks,
     colNA         = "transparent",
     legend.args   = list(text = legendtitle, side = 3, font = 1, line = 0.1, cex = 1.2),
     axis.args     = list(cex.axis = 2, at = legendbreaks, line = 0.1, tick = FALSE, hadj = 0.5, padj = -0.1),
     smallplot     = c(0.4, 0.75, 0.1, 0.15),
     add = T)

dev.off()

```

# Economic Irrigation Potentials

We provide the economic irrigation maps and curves for the 
POT-SUS as well as the POT-UNSUS scenarios.

```{r ReadInEconomic, include=FALSE, echo=FALSE}
# unsustainable land and water
x0    <- collapseNames(IrrigAreaEconPOTUNSUS[, , "0"][, , "off"])
x500  <- collapseNames(IrrigAreaEconPOTUNSUS[, , "500"][, , "off"])
x1000 <- collapseNames(IrrigAreaEconPOTUNSUS[, , "1000"][, , "off"])

# sustainable land and water
x0sus    <- collapseNames(IrrigAreaEconPOTSUS[, , "0"][, , "on"])
x500sus  <- collapseNames(IrrigAreaEconPOTSUS[, , "500"][, , "on"])
x1000sus <- collapseNames(IrrigAreaEconPOTSUS[, , "1000"][, , "on"])
  
```

```{r PlotEconomicPrep, include=FALSE, echo=FALSE}
filename <- "MapEconOfIrrig"

# SUS
potCropland1sus           <- dimSums(collapseNames(IrrigAreaEconPOTSUS[, , "on"]), dim = 1)
getCells(potCropland1sus) <- "GLO"
potCropland1sus           <- data.frame(y = as.numeric(as.character(as.data.frame(potCropland1sus)$Data1)),
                                   x = as.data.frame(potCropland1sus)$Value, stringsAsFactors = FALSE)

# For curve plot
x  <- potCropland1sus$x
y  <- potCropland1sus$y
a1sus <- x[y >= 1000]
b1sus <- y[x == x[y >= 1000]]
a2sus <- x[y <= 1000 & y >= 500]
b2sus <- y[x == x[y <= 1000 & y >= 500]]
a3sus <- x[y <= 500]
b3sus <- y[x == x[y <= 500]]

# UNSUS
potCropland1           <- dimSums(collapseNames(IrrigAreaEconPOTUNSUS[, , "off"]), dim = 1)
getCells(potCropland1) <- "GLO"
potCropland1           <- data.frame(y = as.numeric(as.character(as.data.frame(potCropland1)$Data1)),
                                   x = as.data.frame(potCropland1)$Value, stringsAsFactors = FALSE)

# For curve plot
x  <- potCropland1$x
y  <- potCropland1$y
a1 <- x[y >= 1000]
b1 <- y[x == x[y >= 1000]]
a2 <- x[y <= 1000 & y >= 500]
b2 <- y[x == x[y <= 1000 & y >= 500]]
a3 <- x[y <= 500]
b3 <- y[x == x[y <= 500]]


# PIA
x0[x0 == 0]       <- NA
x500[x500 == 0]   <- NA
x1000[x1000 == 0] <- NA

x0sus[x0sus == 0]       <- NA
x500sus[x500sus == 0]   <- NA
x1000sus[x1000sus == 0] <- NA

# Area correction for map plot
x0[irrigcellshare == 0]    <- NA
x500[irrigcellshare == 0]  <- NA
x1000[irrigcellshare == 0] <- NA

x0sus[irrigcellshare == 0]    <- NA
x500sus[irrigcellshare == 0]  <- NA
x1000sus[irrigcellshare == 0] <- NA

# Legend range adjustment
x0Share    <- x0 / cellarea
x500Share  <- x500 / cellarea
x1000Share <- x1000 / cellarea

x0Sharesus    <- x0sus / cellarea
x500Sharesus  <- x500sus / cellarea
x1000Sharesus <- x1000sus / cellarea

legendtitle  <- "Cellshare"
legendbreaks <- seq(0, 1, 0.25)

### Create and save Legend plot ###
x0_000_025 <- sum(x0[x0Share<0.25 & is.na(x500) & is.na(x1000)], na.rm = TRUE)
x0_025_050 <- sum(x0[x0Share>=0.25 & x0Share<0.5 & is.na(x500) & is.na(x1000)], na.rm = TRUE)
x0_050_075 <- sum(x0[x0Share>=0.5 & x0Share<0.75 & is.na(x500) & is.na(x1000)], na.rm = TRUE)
x0_075_010 <- sum(x0[x0Share>=0.75 & is.na(x500) & is.na(x1000)], na.rm = TRUE)

x500_000_025 <- sum(x500[x500Share<0.25 & is.na(x1000)], na.rm = TRUE)
x500_025_050 <- sum(x500[x500Share>=0.25 & x500Share<0.5 & is.na(x1000)], na.rm = TRUE)
x500_050_075 <- sum(x500[x500Share>=0.5 & x500Share<0.75 & is.na(x1000)], na.rm = TRUE)
x500_075_010 <- sum(x500[x500Share>=0.75 & is.na(x1000)], na.rm = TRUE)

x1000_000_025 <- sum(x1000[x1000Share<0.25], na.rm = TRUE)
x1000_025_050 <- sum(x1000[x1000Share>=0.25 & x1000Share<0.5], na.rm = TRUE)
x1000_050_075 <- sum(x1000[x1000Share>=0.5 & x1000Share<0.75], na.rm = TRUE)
x1000_075_010 <- sum(x1000[x1000Share>=0.75], na.rm = TRUE)

x0_000_025sus <- sum(x0sus[x0Sharesus<0.25 & is.na(x500sus) & is.na(x1000sus)], na.rm = TRUE)
x0_025_050sus <- sum(x0sus[x0Sharesus>=0.25 & x0Sharesus<0.5 & is.na(x500sus) & is.na(x1000sus)], na.rm = TRUE)
x0_050_075sus <- sum(x0sus[x0Sharesus>=0.5 & x0Sharesus<0.75 & is.na(x500sus) & is.na(x1000sus)], na.rm = TRUE)
x0_075_010sus <- sum(x0sus[x0Sharesus>=0.75 & is.na(x500sus) & is.na(x1000sus)], na.rm = TRUE)

x500_000_025sus <- sum(x500sus[x500Sharesus<0.25 & is.na(x1000sus)], na.rm = TRUE)
x500_025_050sus <- sum(x500sus[x500Sharesus>=0.25 & x500Sharesus<0.5 & is.na(x1000sus)], na.rm = TRUE)
x500_050_075sus <- sum(x500sus[x500Sharesus>=0.5 & x500Sharesus<0.75 & is.na(x1000sus)], na.rm = TRUE)
x500_075_010sus <- sum(x500sus[x500Sharesus>=0.75 & is.na(x1000sus)], na.rm = TRUE)

x1000_000_025sus <- sum(x1000sus[x1000Sharesus<0.25], na.rm = TRUE)
x1000_025_050sus <- sum(x1000sus[x1000Sharesus>=0.25 & x1000Sharesus<0.5], na.rm = TRUE)
x1000_050_075sus <- sum(x1000sus[x1000Sharesus>=0.5 & x1000Sharesus<0.75], na.rm = TRUE)
x1000_075_010sus <- sum(x1000sus[x1000Sharesus>=0.75], na.rm = TRUE)

colors <- c("#e5f5e0", "#a1d99b", "#238b45", "#00441b",
          "#deebf7", "#9ecae1", "#4292c6", "#08306b",
          "#fee0d2", "#fc9272", "#cb181d", "#67000d")
values <- c(x0_000_025, x0_025_050, x0_050_075, x0_075_010,
          x500_000_025, x500_025_050, x500_050_075, x500_075_010,
          x1000_000_025, x1000_025_050, x1000_050_075, x1000_075_010)

valuessus <- c(x0_000_025sus, x0_025_050sus, x0_050_075sus, x0_075_010sus,
          x500_000_025sus, x500_025_050sus, x500_050_075sus, x500_075_010sus,
          x1000_000_025sus, x1000_025_050sus, x1000_050_075sus, x1000_075_010sus)

.boxes <- function(position = c(0, 0, 0.25, 1), color = "#e5f5e0", text = "some Mha") {

rect(position[1], position[2], position[3], position[4], border = "black", col = color)
text(mean(c(position[1], position[3])), mean(c(position[2], position[4])), text, cex = 3.5)

}

# Transform magpie object to raster object
x0Share        <- .toolRasterTransform(x0Share)
x500Share      <- .toolRasterTransform(x500Share)
x1000Share     <- .toolRasterTransform(x1000Share)

x0Sharesus        <- .toolRasterTransform(x0Sharesus)
x500Sharesus      <- .toolRasterTransform(x500Sharesus)
x1000Sharesus     <- .toolRasterTransform(x1000Sharesus)
```

```{r PlotEconomicUNSUS, include=FALSE, echo=FALSE}
### Create and save Map plot for UNSUS scenario ###
jpeg(paste0(outputdatapath, filename, "_a.jpeg"), width = 200, height = 120, units = "mm", res = 400)

# Plot Map
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, 
     axes = FALSE)

plot(x0Share, bg = "transparent", ylim = ylim, xlim = xlim, asp = NA, 
     axes = FALSE,
     legend       = FALSE,
     col          = c("#e5f5e0", "#a1d99b", "#238b45", "#00441b"), # green color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add = T)

plot(x500Share, bg = "transparent", ylim = ylim, xlim = xlim, asp = NA, 
     axes = FALSE,
     legend       = FALSE,
     col          = c("#deebf7", "#9ecae1", "#4292c6", "#08306b"), # blue color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add          = T)

plot(x1000Share, bg = "transparent", ylim = ylim, xlim = xlim, asp = NA, 
     axes = FALSE,
     legend       = FALSE,
     col          = c("#fee0d2", "#fc9272", "#cb181d", "#67000d"), # red color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add          = T)

plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)

title("a) POT-UNSUS", cex.main = 1.5, line = 0.5, adj = 0)

dev.off()
```

```{r PlotEconomicSUS, include=FALSE, echo=FALSE}
### Create and save Map plot for SUS scenario ###
jpeg(paste0(outputdatapath, filename, "_b.jpeg"), width = 200, height = 120, units = "mm", res = 400)

# Plot Map
par(mar = c(0, 0, 0, 0), oma = c(0, 0, 0, 0))
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)

plot(x0Sharesus, bg = "transparent", ylim = ylim, xlim = xlim,
     asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = c("#e5f5e0", "#a1d99b", "#238b45", "#00441b"), # green color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add = T)

plot(x500Sharesus, bg = "transparent", ylim = ylim, xlim = xlim,
     asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = c("#deebf7", "#9ecae1", "#4292c6", "#08306b"), # blue color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add          = T)

plot(x1000Sharesus, bg = "transparent", ylim = ylim, xlim = xlim,
     asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = c("#fee0d2", "#fc9272", "#cb181d", "#67000d"), # red color scale
     breaks       = legendbreaks,
     colNA        = NA,
     add          = T)

plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)

title("b) POT-SUS", cex.main = 1.5, line = 0.5, adj = 0)

dev.off()
```

```{r PlotEconomicCurve, include=FALSE, echo=FALSE}
# Curve Plot
pdf(paste0(outputdatapath, filename, "_c.pdf"), height = 9, width = 26)

par(fig = c(0.03, 0.45, 0, 1), bg = "white", new = FALSE,
  mar = c(7, 7, 5, 1), xaxs = "i", yaxs = "i")
plot(x, y, bg = "white",
   col = ifelse(y > 1000, "#cb181d", ifelse(y > 500, "#08306b", "#238b45")),
   main = "",
   xlab = "",
   ylab = "",
   cex.lab = 3.5,
   type = "p", pch = 19, lty = 1, lwd = 2.5,
   bty = "l", yaxt = "n", xaxt = "n")
s <- seq(length(a1)-1)
segments(a1[s], b1[s], a1[s+1], b1[s+1], col= "#cb181d", lwd = 8)
s <- seq(length(a2)-1)
segments(a2[s], b2[s], a2[s+1], b2[s+1], col= "#08306b", lwd = 8)
s <- seq(length(a3)-1)
segments(a3[s], b3[s], a3[s+1], b3[s+1], col= "#238b45", lwd = 8)
text(1000, 750, "POT-UNSUS", col = "black", cex = 3)

s <- seq(length(a1sus)-1)
segments(a1sus[s], b1sus[s], a1sus[s+1], b1sus[s+1], col= "#fc9272", lwd = 8)
s <- seq(length(a2sus)-1)
segments(a2sus[s], b2sus[s], a2sus[s+1], b2sus[s+1], col= "#9ecae1", lwd = 8)
s <- seq(length(a3sus)-1)
segments(a3sus[s], b3sus[s], a3sus[s+1], b3sus[s+1], col= "#a1d99b", lwd = 8)
text(450, 300, "POT-SUS", col = "black", cex = 3)

axis(side = 1, cex.axis = 3, hadj = 0.5, padj = 0.5,
   at = c(seq(from = 0, to = max(potCropland1$x),by = 200))) # x axis
axis(side = 2, cex.axis = 3, hadj = 1, padj = 0.5,
   at = c(seq(from = 0, to = 3000, by = 500)), las = 1)      # y axis
mtext("Irrigation yield gain (in USD/ha)", side = 2, line = 7, cex = 3.5)
mtext("Irrigated area (in Mha)", side = 1, line = 5.5, cex = 3.5)
#title("Global \nIrrigation Area Potential \non potential cropland", cex.main = 3, line = -5, adj = 0.1)
title("c)", cex.main = 4.5, line = 2, adj = 0)

# Legend UNSUS
par(mar = c(1, 1, 1, 1), fig = c(0.5, 0.98, 0.6, 0.9), new = TRUE)
plot(c(0, 1), c(0, 3), type = "n", xlab = "", ylab = "", axes = FALSE)
axis(side = 1, col = NA, col.ticks = NA, at = legendbreaks, cex.axis = 3, padj = 0.6)
axis(side = 2, col = NA, col.ticks = NA, at = c(1, 2, 3), cex.axis = 3,
   hadj = 1, padj = 1.4, c(">0-500 USD/ha", ">500-1000 USD/ha", ">1000 USD/ha"), las = 2)
mtext("POT-UNSUS", side = 3, line = 0.5, cex = 3.8)

i <- 0
for (threshold in c(1, 2, 3)) {
for (share in c(0.25, 0.5, 0.75, 1)) {
  i <- i + 1
  .boxes(position = c(share-0.25, threshold-1, share, threshold),
         color = colors[i], text = paste0(round(values[i]), " Mha"))
 }
}

# Legend SUS
par(mar = c(1, 1, 1, 1), fig = c(0.5, 0.98, 0.15, 0.45), new = TRUE)
plot(c(0, 1), c(0, 3), type = "n", xlab = "", ylab = "", axes = FALSE)
axis(side = 1, col = NA, col.ticks = NA, at = legendbreaks, cex.axis = 3, padj = 0.6)
axis(side = 2, col = NA, col.ticks = NA, at = c(1, 2, 3), cex.axis = 3,
   hadj = 1, padj = 1.4, c(">0-500 USD/ha", ">500-1000 USD/ha", ">1000 USD/ha"), las = 2)
mtext("Cell share", side = 1, line = 6, cex = 3.8)
mtext("POT-SUS", side = 3, line = 0.5, cex = 3.8)
i <- 0
for (threshold in c(1, 2, 3)) {
for (share in c(0.25, 0.5, 0.75, 1)) {
  i <- i + 1
  .boxes(position = c(share-0.25, threshold-1, share, threshold),
         color = colors[i], text = paste0(round(valuessus[i]), " Mha"))
 }
}

dev.off()

```


# Supplementary Material

## Discharge Accessibility

The more variable the discharge, the harder it is accessible to humans. This graph visualizes the relationship between discharge and accessibility.

```{r FunctionalRelationshipGraph, include=FALSE, echo=FALSE}
# Inputdata
input <- "LPJmL_monthlyDischarge"

# Read in data
monthlyD <- read.magpie(paste0(inputdatapath, input, ".mz"))
coeff    <- 2

# Extract years
years <- getYears(monthlyD, as.integer = TRUE)
if (class(year) != "numeric") {
  year <- as.numeric(gsub("y", "", year))
}

for (y in year) {

  # Long-term reference time frame for discharge variability calculation
  if ((y - 30) > years[1]) {
    longterm_period <- seq(y - 30, y, by = 1)
  } else {
    longterm_period <- seq(1980, 2010, by = 1)
  }
  monthly_discharge <- monthlyD[, longterm_period, ]

  # Transform to array (faster calculation)
  monthly_discharge <- as.array(collapseNames(monthly_discharge))

  ### Variation Coefficient Method ###
  # Mean and standard deviation of discharge
  mean_discharge <- apply(monthly_discharge, MARGIN = 1, mean)
  std_discharge  <- apply(monthly_discharge, MARGIN = 1, sd)

  # Coefficient of Variation
  cv <- ifelse(mean_discharge > 0, std_discharge / mean_discharge, 0)
}

x <- seq(min(cv), max(cv), by = 1)

### Create and save plot ###
pdf(paste0("outputs/AccessibilityRule.pdf"), height = 21.0, width = 29.7, paper = "a4r")
par(mfrow = c(2, 1),
    mar = c(4.1, 4.1, 4.1, 2.1))

hist(cv, breaks = 100, main = NULL,
     xlab = "Coefficient of variation of monthly discharge (std.deviation/mean)",
     ylab = "Frequency (Number of grid cells)",
      #ylim = c(0,19),
     yaxs = "i",
    col = "lightblue")
axis(side = 1, at = seq(min(cv), max(cv), by = 1)) # x axis
title("(a)", adj = 0)

plot(coeff^(-x),
   type = "l",
   xlab = "Coefficient of variation of monthly discharge (std.deviation/mean)",
   ylab = "Accessible share of discharge",
   cex.lab = 1,
   xlim = c(min(x), max(x)), ylim = c(0, 1),
   #xaxs = "i",
   yaxs = "i",
   lwd = 4, col = "blue")
axis(side = 1, at = seq(min(cv), max(cv), by = 1)) # x axis
axis(side = 2, at = seq(0, 1, by = 0.1))  # y axis
title("(b)", adj = 0)

dev.off()

```

## Protected Areas according to Half Earth Scenario

```{r ProtectedAreaReadin, include=TRUE, echo=FALSE}
potlandUnprotect <- read.magpie(paste0(inputdatapath, "avlIrrigarea_pot.mz"))

print(paste0("Non-protected areas that are suitable for cropland activities: ", dimSums(potlandUnprotect, dim = 1)))
```

The Protected Areas map shows the share of each grid cell that is protected following the Half Earth scenario. 

```{r HalfEarth, include=FALSE, echo=FALSE}
protectSCEN <- "HalfEarth"

# Read in data
protectArea <- collapseNames(read.magpie(paste0(inputdatapath, "protectedAreas.mz"))[, , protectSCEN])

# Cell share that is protected
protectArea <- protectArea / cellarea
protectArea[protectArea > 1] <- 1

# Plot Fulfilled Share
legendtitle  <- "Protected Share"
legendbreaks <- seq(0, 1, 0.1)
legendcolor  <- c("#FFFFFF", "#f7fcb9", "#e5f5e0", "#c7e9c0", "#a1d99b",
                  "#74c476", "#41ab5d", "#238b45", "#006d2c", "#00441b")

# Transform magpie object to raster object
protectArea <- .toolRasterTransform(protectArea)
# correct rounding
protectArea[protectArea < 0] <- 0
protectArea[protectArea > 1] <- 1

jpeg(paste0(outputdatapath, "ProtectArea", ".jpeg"), width = 8, height = 4.5, units = "in", res = 400)

plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
plot(protectArea, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = legendcolor,
     breaks       = legendbreaks,
     colNA        = colNA,
     add          = T)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)

# Legend
plot(protectArea, bg = "transparent",
     legend.only   = TRUE,
     horizontal    = TRUE,
     col           = legendcolor,
     breaks        = legendbreaks,
     colNA         = "transparent",
     legend.args   = list(text = legendtitle, side = 3, font = 1, line = 0.5, cex = 1),
     axis.args     = list(cex.axis = 1, at = legendbreaks, line = 0, tick = FALSE, hadj = 0.4, padj = -1.2),
     smallplot     = c(0.4, 0.75, 0.1, 0.15),
     add = T)

dev.off()

```

## Yield gain (in USD/ha)

```{r YieldGain, include=TRUE, echo=FALSE}

# Read in data
yieldGain   <- dimSums(read.magpie(paste0(inputdatapath, "yieldgain_USDha", ".mz")), dim = 3)
getSets(yieldGain) <- c("x", "y", "iso", "year", "data")

# Dummy variables for land extent:
tmpIrrig                      <- LUHirrigated
tmpIrrig[tmpIrrig != 0]       <- 1
tmpIrrig                      <- yieldGain * tmpIrrig

tmpCropland                   <- LUHtotal
tmpCropland[tmpCropland != 0] <- 1
tmpCropland                   <- yieldGain * tmpCropland

tmpPotTotal                   <- collapseNames(yieldgainareaPOTunsus[,,"0"])
tmpPotTotal[tmpPotTotal != 0] <- 1
tmpPotTotal                   <- yieldGain * tmpPotTotal

tmpPotSus                     <- collapseNames(yieldgainareaPOTsus[,,"0"])
tmpPotSus[tmpPotSus != 0]     <- 1
tmpPotSus                     <- yieldGain * tmpPotSus

# In-text numbers (global)
writeLines(paste0("The average yield value gain on currently irrigated areas is ", round(mean(tmpIrrig), digits = 1), "USD per hectare. \nIt ranges between ", round(min(tmpIrrig)), " and ", round(max(tmpIrrig)), "USD per hectare. The median is: ", round(median(tmpIrrig)), ". ",
"\nThe average yield value gain on current cropland is ", round(mean(tmpCropland), digits = 1), "hectare. \nIt ranges between ", round(min(tmpCropland)), " and ", round(max(tmpCropland)), "USD per hectare. The median is: ", round(median(tmpCropland)), ". ", 
"\nThe average yield value gain on total potential cropland is ", round(mean(tmpPotTotal), digits = 1), ". \nIt ranges between ", round(min(tmpPotTotal)), " and ", round(max(tmpPotTotal)), "USD per hectare. The median is: ", round(median(tmpPotTotal)), ". ", 
"\nThe average yield value gain on potential (unprotected) cropland is ", round(mean(tmpPotSus), digits = 1), ". \nIt ranges between ", round(min(tmpPotSus)), " and ", round(max(tmpPotSus)), "USD per hectare. The median is: ", round(median(tmpPotSus)), ". "))

# Set 0 to NA:
yieldGain[yieldGain <= 0] <- NA

# Legend
legendbreaks <- c(0, 100, 300, 500, 700, 900, 1000)
legendcolor <- c("#FFFFFF", "#fdbb84", "#fc8d59", "#d7301f", "#b30000", "#7f0000")

# Transform magpie object to raster object
yieldGain <- .toolRasterTransform(yieldGain)

yieldGain[yieldGain < 0]     <- 0
yieldGain[yieldGain >= 1000] <- 999

jpeg(paste0(outputdatapath, "Yields", ".jpeg"), width = 8, height = 4.5, units = "in", res = 400)

plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE)
plot(yieldGain, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE,
     legend       = FALSE,
     col          = legendcolor,
     breaks       = legendbreaks,
     colNA        = colNA,
     add          = T)
plot(landMask, border = "white", col = "white", ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)
plot(worldCountries, ylim = ylim, xlim = xlim, asp = NA, axes = FALSE, add = T)

# Legend
plot(yieldGain, bg = "transparent",
     legend.only   = TRUE,
     horizontal    = TRUE,
     col           = legendcolor,
     breaks        = legendbreaks,
     colNA         = "transparent",
     legend.args   = list(text = "USD per ha", side = 3, font = 1, line = 0.5, cex = 1),
     axis.args     = list(cex.axis = 0.8, at = legendbreaks, line = 0, tick = FALSE, hadj = 0.4, padj = -1.5),
     smallplot     = c(0.4, 0.75, 0.1, 0.15),
     add = T)

dev.off()

```

